\papertitle

### 2012-10-11 manuscript.tex
Figure improvements and grouping for path and feasible set

%TODO make these span the page, with identical scales/style
\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{figures/flight_paths.pdf}
\caption{Plot of camera field-of-view and H$^2$Bird minimum turning radius 
cone, with experimental trials overlayed.}
\label{fig:flight_paths}
\end{minipage}
\end{figure*}

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/flight_paths_feasible.pdf}
\caption{Plot of camera field of view and experimental trials within the feasible region.}
\label{fig:flight_paths_feasible}
\end{figure}

>>>>

%TODO make these span the page, with identical scales/style
\begin{figure*}[tb]

\begin{minipage}{\linewidth}
\centering
\includegraphics[width=0.45\textwidth]{figures/feasible_set.pdf}
\caption{Plot of camera field-of-view and backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\vspace{1em}
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{figures/flight_paths_feasible.pdf}
\caption{Plot of camera field of view and experimental trials within the feasible region.}
\label{fig:flight_paths_feasible}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{figures/flight_paths.pdf}
\caption{Plot of camera field-of-view and perimeter experimental trials overlayed.}
\label{fig:flight_paths}
\end{minipage}
\end{figure*}
